% CREATED BY DAVID FRISK, 2015
An Informative Headline describing the Content of the Report\\
A Subtitle that can be Very Much Longer if Necessary\\
NAME FAMILYNAME\\
Department of Applied Information Technology\\
Chalmers University of Technology \setlength{\parskip}{0.5cm}

\thispagestyle{plain}			% Supress header 
\setlength{\parskip}{0pt plus 1.0pt}
\section*{Abstract}
Data is a hot subject of today, and the storage, security and accessibility of this data is essential for all digital companies. Established companies have no problems spending large amounts on research and development of data storage solutions. However, smaller companies or startups are facing similar problems with a lot less capital to support the research. 
\\[0.5cm]
This bachelor's thesis is based on testing and analyzing database storage technologies. Realistic test cases will be created from three companies that has been chosen for their particular field. The test cases will be run on identical hardware yet various software. The five different technologies have also been chosen to represent the majority of solutions that exist today. 
\\[0.5cm]
The findings will be compiled into a web page with easy access and understandable contents. The comparison of databases is not a ground breaking area, but the findings are often presented in long and complex papers. We are trying to bring these complex findings and serve them in an easier fashion.

% KEYWORDS (MAXIMUM 10 WORDS)
\vfill
Keywords: lorem, ipsum, dolor, sit, amet, consectetur, adipisicing, elit, sed, do.
