% CREATED BY DAVID FRISK, 2015
\chapter{Methods}
The project was divided into three phases: a pre-study, implementation of the different database techniques and the testing. The main focus during the pre-study was familiarizing with the various database techniques, particularly NoSQL databases, and explore the different types of data the companies are storing.\\
In addition, to obtain a realistic insight on how start-up companies manage their application data and how their initial database technology were selected, interviews were conducted with startups at Chalmers Ventures, in Gothenburg. 
\\[0.5cm]
Next phase in the project was to setup virtual machines with the selected database technologies. With the help of the pre-study and collected data from companies, scenarios and test cases was created to test on the different virtual machines. Parameters as time per operation, total elapsed time, and the performance heavy operations were running for testing the machines.  
\\[0.5cm]

\section{Pre-study}

\section{Companies}
\todo[inline]{Vi behöver få in vad de skall använda för data. Även hur de arbetar med skalning och deras tillväxt. Detta skall ligga i METOD och vi skall även bygga in hur vi skall använda företagen då. }
% Erik

Short description of the companies we are working with and how they represents the general "company".
\subsection{SKIM}
% Taskman
Skim is an international market analysis company to help other companies with pricing and portfolio management. Skim has more than 100 employees and their headquarter is located in Rotterdam.
Skim has existed in more than 35 years, but their CRM solution has not published yet and is under developing.
Skims role in the project is to be the general company with large amount of images and lists linked to different users and projects. %to be continued

\subsection{RaceONE}
% Joakim
RaceONE is a startup company from Gothenburg with five employees. Their product is a mobile application for sharing and following different sport races live.
RaceONE's role in the project is to be the general company with real time data in terms of coordinates.  
\subsection{Reddit}
% Arneson

\section{Interviews with startups at Chalmers Ventures}
% Pedram
At an early stage of the project it was decided by the group to visit Swedish-based startup companies, in order to obtain a realistic insight on how different companies handle their application data. Five companies at Ventures in Gothenburg were interviewed and questions that were posed are the followings:
\\[0.5cm]
Questions posed to the companies:

\begin{itemize}
\item What type of data is your company storing primarly? 
\item Another entry in the list
\end{itemize}

\section{Agile development}
% Viktor
Scrum, Sprints,...
\subsection{Sprint planning}
% Viktor
The models of each company.
\subsection{Tools}
% Viktor
Trello (labels, backlog, features, testing...)

\section{Internal lectures}
% Erik
The models of each company.

To get a broader knowledge of the various database technologies included in the research, the group members took turns to lecture each other. Every member was assigned to one technology they need to read up on.


\section{Testing}
AAA
\subsection{Test cases}
% Arneson
Explain why we are creating test cases and also how we can come up with realistic ones (think: company aid, research...). Also explain how we will present the results of the test cases.
\newline\newline
<Table of test cases> These should maybe be in the appendix.
\subsection{Virtual Machines}
% Kloakim
Explain Digital Ocean, how we set up the machines and how we can assure they represent the reality.
\subsection{Company models}
% Arneson & Kloakim
Explain how we created models for the companies.

\section{Software development}
Short about our approach.
\subsection{RaceONE}
Go through the development of RaceONE.
\subsection{SKIM}
%
%The development with Skim is to create an image uploader module in their platform. The platform is a CRM-system to help their work with market analysis. 
%The platform is built in the Mean stack, which includes Mongodb, Express, Angular and Node.
%The image uploader module will have more functionality than just uploading images. It will also making
%
\section{Application flow}
% Arneson
Explain the flow in the portals.

\section{Analysis report}
We will present the analysis with a illustrative website. We are doing this because it is clearer way to deliver our results to a startup instead of a long formal report. 

\section{Delimitations}
How are we going to write the tests?
